\documentclass[12]{amsart}
\begin{document}
    \title{Ross Counselor Application}
    \author{Sean Richardson}
    \maketitle
    
    \begin{enumerate}
        \item I can attend all days of the U.S. program (June 20-July 31), and all days of the relocated Asia program (July 5-August 7) if the dates stay approximately the same. I would enjoy working at either program.\\
        \item 
            \begin{itemize}
                \item Legal name: Sean Richardson
                \item Gender: Male
                \item Birthdate: 09/24/1998 (21 years old).
                \item My hometown is Portland, OR and I attended high school at La Salle Catholic College Preparatory in Portland, OR.
                \item Email address: seanhrichardson@gmail.com\\
            \end{itemize}
        \item Citizenship: U.S.\\
        \item Education: Lewis \& Clark College in Portland, OR.\\
            (Dates: \textit{September 2016 --- May 2020 expected}).\\
            Bachelor of Arts in Mathematics and Computer Science.\\
            Bachelor of Arts in Physics.\\

        \item As a high schooler, I did not participate in any math camps or
            math competitions. However, I did compete in the 2018 and 2019
            Putnam competitions. I scored 20 points this past competition,
            which is not outstanding, but perhaps shows I have some familiarity with olympiad style techniques, topics, and approaches. Further, I have three
            years of experience in working as a peer tutor at the math resource center at Lewis \& Clark and experience grading for math and physics classes, including discrete mathematics. \\

        \item I plan on applying to graduate schools in mathematics this coming fall where I will likely study differential geometry, topology, optimization, or perhaps something else that peaks my interest. I enjoy teaching, so working towards professorship would be ideal, but I will reassess my interests and career goals after completing graduate school. \\

    \item I have done formal course work in both number theory and abstract
        algebra. Specifically, I am currently taking the second semester of a
        year-long sequence in abstract algebra at Lewis \& Clark College, and        I took a number theory course in the Budapest Semesters in
        Mathematics 2019 Summer Program. In looking at the Ross number theory topics, I have had course work in every topic up to and including the ``finite fields'' section. I also seen Minkowski's theorem and the geometric proofs of the two square and four square theorems in my BSM number theory course. I believe I am mathematically experienced enough that I could learn the few topics I am unfamiliar with quickly.\\

    \item 
        I find differential geometry interesting especially in connection to physics. Recently however, I have gotten interested in topology, which appears to be full of rich and complex questions stemming from simple definitions.

        I have done research in differential geometry studying the Laplace equation on orbifolds. In fact, I published a paper with my advisor: ``You can hear the local orientability of an orbifold'' in the journal \textit{Differential Geometry and its Applications}. I am also in my second semester of an independent study on topological K-Theory. While I am far from ready to do any research in this area, I am practicing my ability to read and understand graduate level material.\\

    \item While I am naturally more reserved, I can still be welcoming, social,
        and enthusiastic when the situation calls for it. \\
        Through my time on
        the Lewis \& Clark cross country team, I have had plenty of practice
        welcoming new members and making them feel at home before they have
        settled into college life. Similarly, I would often host prospective high school runners interested in coming to Lewis \& Clark and make the high schoolers feel comfortable in a new environment.

        While I have had not had any formal experience or training in helping people work through personal crises, my friends regard me as a good person to talk to and I am confident that I could offer a helpful conversation and perhaps some guidance to a high schooler that is working through something.

        Additionally, I have worked at the mathematics tutoring and resource center at my college, giving me experience in providing encouragement and guidance in mathematics situations.
        
        And, I am certainly eager to give impromptu math lectures to interested students. In fact, after all the complaints from friends and family, it would be a pleasant change to lecture to an interested audience!\\

    \item Interests and hobbies:\\
        Outside of academic work, I have a passion for distance running! I find running relaxing and refreshing, but I am also drawn to the competitive nature of running and the need for self improvement. I have compete on the Lewis \& Clark cross country and track teams for four years and I currently run 70 miles a week; I hope to continue running after graduating and perhaps work towards marathon running.
        
        I also have an interest in chess! I only casually play chess and rarely study chess formally, but I recently helped found the Lewis \& Clark chess club and I am always up for a game of chess.

    \end{enumerate}
\end{document}
