\documentclass[12]{amsart}

\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{mathtools}

\DeclareMathOperator{\vect}{Vect} 


\begin{document}
\section{Category Theory}%CATEGORY THEORY:
\begin{enumerate}
    \item Definition of Category Theory \label{cat_theory}
    \item homomorphism, monomorphism, epimorphism, isomorphism, automorphism?
    \item Category of Sets
    \item Category of Rings

\section{Linear Algebra}%LINEAR ALGEBRA:
    \item Category of Vector Spaces 
    \item Direct sum on V.S. definition
    \item Complentary Definition
    \item Tensor product on V.S. definition

\section{Topology}%TOPOLOGY
    \item Category of Toplogical Spaces (\ref{cat_theory})
    \item Hausdorff and Normal definitions [???]
    \item Tietze Extension Theorem \label{tietze} [???]
    \item Homotopy things \label{homotopy}
        \begin{enumerate}
            \item Homotopic functions
            \item Homotopy equivalence of spaces 
            \item Retraction definition
            \item Contractible definition \label{contractible}
        \end{enumerate}
    \item Operations on topological spaces: \label{top_ops}
        \begin{enumerate}
            \item Topological quotient
            \item Wedge Sum
            \item Smash Product
            \item Cone and Suspension
        \end{enumerate}

\section{Vector Bundles} %VECTOR BUNDLES
    \item Category of vector bundles 
    \item Definition of V.B.
    \item Definitions of $\Gamma(E)$, homomorphism, isomorphism. \label{vect_morph}
    \item Restriction and pullback of bundles
    \item Applying functor $T$ on vector spaces to functor on vector bundles [make less abstract?] [Need $\oplus$, $\otimes$, anything else?].
        \begin{itemize}
            \item Do concretely for one and introduce others as an exercise?
        \end{itemize}
        \begin{enumerate}
            \item Definition of $T$ on bundles
            \item Verify $T(E)$ has natural topology and $T(\varphi)$ is continuous.
        \end{enumerate}
    \item Sub-bundle definition [???]
    \item Quotient bundle definition (\ref{top_ops}) [???]
    \item Hermetian bundle and metric on bundle definition [???]
    \item Bundle form of Tietze Extension Theorem (\ref{tietze}) \label{tietze_vb} [???]
    \item Collapsing Operation (Lemma 1.4.7) (\ref{vect_morph}, \ref{top_ops}, \ref{homotopy})
    \item Gluing/Clutching Construction (\ref{vect_morph}, \ref{top_ops})

    \section{Definition of K-Theory (and reduced K-Theory?)} %K-THEORY:
    \item Definition of $\vect(X)$ (\ref{vect_morph}) \label{vect}
    \item $\vect(X)$ equipped with $\oplus$ and $\otimes$. \label{vect_ops} 
    \item Stably isomorphic definition. (\ref{vect_ops}) $\label{iso_stab}$
    \item Group/Ring Completion through Universal Property \label{completion}
    \item Definition of K(X) [and $\tilde{K}(X)$?] (\ref{vect}, \ref{completion}, \ref{iso_stab}).
    \begin{itemize}
        \item Verify relevant equivalence relations.
        \item Computation of $K(X)$ and $\tilde{K}(X)$ for contractible bundles?
        \item Proof of equivalence of multiple definitions. (Present one way and introduce another as an exercise).
    \end{itemize}

\section{K-Theory as a cohomomology theory}
    \item $f_t: Y \to X$ homotopy then $f_0^*E \cong f_1^*E$. \label{homotopy_iso} (\ref{homotopy})
    \item If $f: X \to Y$ is a homotopy equivalence, $f^*: \vect(X) \to \vect(Y)$ is bijective. (Lemma 1.4.4 in Atiyah) (\ref{homotopy_iso})
    \item Contractible $Y$ and $f: X \to X/Y$ induces bijection $f^*: \vect(X/Y) \to \vect(X)$ (Lemma 1.4.8 in Atiyah, Lemma 2.10 in Hatcher) (\ref{contractible}, \ref{vect})
    \item Exact sequences
    \begin{enumerate}
        \item Definition of exact sequence of vector spaces
        \item Definition of exact sequence of vector bundles
        \item (?) If short exact sequence $0 \to E' \to E \to E'' \to 0$ then $E \cong E' \oplus E''$
    \end{enumerate}
    \item Bott Periodicity Theorem

\section{Division Algebra Application} %DIVISION ALGEBRAS APPLICATION:

\end{enumerate}

\section{Other}

\begin{itemize}
    \item V.B. homomorphism is isomorphism iff bijective
    \item Strict homomorphism definition
    \item $\Gamma(E)$ is a V.S.
    \item Prop 1.3.2 (Ker, Im, Coker and sub bundles)
    \item Natural isomoprhism $f^*T(E) \cong Tf^*(E)$
    \item Projection operator definition
    \item Fundamental Product Theorem in Hatcher
\end{itemize}

\section{Notes/Questions on Outline}
\begin{itemize}
    \item How much time should I spend on vector bundles?
    \item Try to talk about vector bundles with manifolds?
    \item Category of sets as example?
    \item Should I lean to abstract or to concrete? I'm thinking concrete.
\end{itemize}

\section{Questions on Material}
\begin{itemize}
    \item Stably isomorphic classes vs. group completion of $\vect(X)$.
    \item Wedge Sum, smash product, cone, suspension.
\end{itemize}

\end{document}
