\documentclass[12pt]{amsart}

\setlength{\parindent}{0cm}
\usepackage[margin=1in]{geometry}

\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{float}
\usepackage{enumitem}
\usepackage{commath}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{cancel}
\usepackage{subfigure}
\usepackage{multicol}
\usepackage{gensymb}

\usepackage{graphicx}
\graphicspath{{graphics/}}

\usepackage{my_notes}
\usepackage{my_math}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{technique}[theorem]{Technique}

\newenvironment{just}{\textit{Justification.}}{}
\newenvironment{trans}{\textit{Translation.}}{}

\newenvironment{mybox}
{\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black]}
{\end{tcolorbox}}

\newenvironment{mytbox}[1]
{\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=#1]}
{\end{tcolorbox}}

\def\mathunderline#1#2{\color{#1}\underline{{\color{black}#2}}\color{black}}

\begin{document}
\title{Conjecture \& Proof}
\author{Sean Richardson}
\date{\today}
\maketitle


\section{Non Existence / ``Show it is impossible'' Proofs}
\begin{technique}[Invariant]
Find an invariant --- some value that is impossible to change
        sufficiently.    
\end{technique}
Problems:
\begin{enumerate}
    \item Show it is impossible to get from $4$ to $6$ using the operations $n \rightarrow
        n^2$, $n \rightarrow 2^n$ and $n \rightarrow n-49$.
    \item 
\end{enumerate}
\begin{technique}[Contradiction]
    Proof by contradiction. Assume that it does exist. This will give some
    information to work with in order to generate a contradiction. 
    \\Note: when possible, it does not hurt to assume some extra
    information such that the assumption is in some kind of minimal form. 
\end{technique}
\section{Existence Proofs}
\begin{technique}[Directly]
    Provide an example. Done.
\end{technique}


\section{Other Techniques}
\begin{technique}
    To arrive at a contradiction, generate a sequence $a_n$ such that $a_n
    \rightarrow 0$ but that we can place a lower bound on. Note: the fact
    $a \in \mathbb{Z}, a > 0 \implies a \geq 1$ is often useful.
\end{technique}
\begin{enumerate}
    \item Show $\sqrt{2}$ is irrational. (Can take sequence $a_n =
        (1-\sqrt{2})^n$).
\end{enumerate}

\begin{technique}[This or That]
    Conclude that one thing in some set of things must be true. AND, in the
    whole set of things, the claim must hold.
\end{technique}
\begin{enumerate}
    \item Show there exists $a,b \notin \mathbb{Q}$ such that $a^b \in
        \mathbb{Q}$. Hint: consider ${\left(
        \sqrt{2}^\sqrt{2}\right)}^\sqrt{2}$
\end{enumerate}

\end{document}
